---
title: "Titanic Survival Analysis"
author: "Fredrick Stakem"
date: "October 20, 2014"
output: ioslides_presentation
---

## Background Information

- Titanic is well known disaster but few people know the details
- There is a clear seperation of groups from data given on a popular Kaggle competition
- A simple analysis shows men and 3rd class passengers much more likely to die
- Even more complex analysis can be performed across many different features

```{r, echo=FALSE}
library(ggplot2)
training_data <- read.csv('../raw_data/train.csv')
```



## Survival by Gender

```{r, echo=FALSE}
data <- training_data[, c('Sex', 'Survived')]
gender_data <- table(data$Survived, data$Sex)
        
barplot(gender_data, 
        ylab="People",
        xlab="Gender", 
        beside=TRUE,
        col=c("lightblue3","darkolivegreen4"),
        legend = c('Died', 'Survived'),
        names.arg=c("Female", "Male"))
```

## Survival by Ticket Class

```{r, echo=FALSE}
data <- training_data[, c('Pclass', 'Survived')]
survival_data <- table(data$Survived, data$Pclass)
            
barplot(survival_data, 
        ylab="People",
        xlab="Class", 
        beside=TRUE,
        col=c("lightblue3","darkolivegreen4"),
        legend = c('Died', 'Survived'),
        names.arg=c("1st", "2nd", "3rd"))
```

## Survival by Age

```{r, echo=FALSE}
data <- training_data[, c('Age', 'Survived')]
data <- na.omit(data)
row.names(data)<-NULL
translation <- data.frame(Values=c(0, 1), Result=c('Died', 'Survived'))
data <- merge(data, translation, by.x='Survived', by.y='Values')[,-1]

ggplot(data, aes(x=Age, colour=Result, fill=Result)) + 
    geom_density(alpha=.3) +
    ggtitle("Passager Survival Likelihood based Upon Age")
```

